---
title: 'Dublin City Marathon 2019: Analysis with R'
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(xml2)
library(rvest)
library(plyr)
library(dplyr) #
```


## Get the data

Full results for the Dublin Marathon were scraped from tables on a website. (180 tables with 100 entrants on each table.) Tables were compiled into a list called 'list.of.dataframes'.

```{r Scraping the data}

# Set up an empty list to store our downloaded tables.
list.of.dataframes <- vector("list",180)

# Store the URL in a variable, minus the page number:
url <- "https://www.tdleventservices.co.uk/event-results/events?event=3492&page="

# Now we loop through 180 pages; add each page number to the URL; extract and store the data.
page <- 177
while (page <=180){
  list.of.dataframes[[page]] <-
    paste(url,page,sep="") %>%
    read_html() %>%                                                                     # xml2
    html_nodes(xpath='/html/body/div[2]/div/div/div/div/div[2]/div[2]/table') %>%       # rvest
    html_table() %>%                    
    data.frame()
  page <- page + 1
  Sys.sleep(5) # Pause 45s after downloading each table, to avoid being mistaken for mischief-maker.
}
```

Once all are downloaded, bind all the results into a single dataframe.

```{r}

all.results.df <- rbind.fill(list.of.dataframes)                                         # plyr  

```

Error: Column `Gender.Position` can't be converted from integer to character

This is because some of the columns that contain mostly numeric data also contain 'DNF' (did not finish) for the runners who didn't reach the finish line.

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
